Analysis paper

### 2021-06-25 analysis/analysis.Rmd
update plots

```{r}
df <- copy(dailytruth_data)[
  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
]

@@

df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  # geom_point(size = 0.3, alpha = 0.4) + 
  # geom_line(size = 0.5, alpha = 0.4) + 
  geom_col(fill = "lightsteelblue", color = "white") + 
  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                          max(forecast_dates$full_hub_period + 21))) + 
  theme_minimal()

@@

p <- ens[, .(value = sum(value), 
             epinow = sum(epinow, na.rm = TRUE), 
             crowd = sum(crowd, na.rm = TRUE)), by = c("variable", "Date")] %>%
  ggplot(aes(y = value, x = Date, color = variable)) + 
  geom_point()

>>>>

```{r}
df <- copy(dailytruth_data)[
  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
][, target_end_date := as.Date(target_end_date)
]

df[weekdays(target_end_date) == "Sunday", sundays := target_end_date]

@@

df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  # geom_point(size = 0.3, alpha = 0.4) + 
  # geom_line(size = 0.5, alpha = 0.4) + 
  geom_col(fill = "lightsteelblue", color = "white") + 
  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
  # geom_vline(aes(xintercept = sundays), linetype = "dashed", alpha = 0.2) + 
  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                          max(forecast_dates$full_hub_period + 21))) + 
  theme_minimal()

@@

p <- ens[, .(value = sum(value), 
             epinow = sum(epinow, na.rm = TRUE), 
             crowd = sum(crowd, na.rm = TRUE)), by = c("variable", "Date")] %>%
  ggplot(aes(y = value, x = Date, color = variable)) + 
  # geom_col(aes(fill = variable), position = position_dodge()) + 
  geom_point() + 
  geom_line() + 
  scale_color_manual(values = colcases) + 
  theme_minimal()
